\documentclass[10pt]{article}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage[margin=2cm,includefoot]{geometry}
%%%Header and footer stuff
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[table, dvipsnames]{xcolor}
%\graphicspath{/home/mohammad/Template/My Report Template/Images}
\usepackage{float}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{lipsum}
%\fancyfoot{}
%\fancyfoot[R]{\thepage}
%%%

\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}

\newcommand\tab[1][0.5cm]{\hspace*{#1}}


%\rhead{Daneshvar Garmroodi, Mohammad Reza}
%\lhead{Experiences and Achievments}


\begin{document}
	
	\begin{center}
		{\color{violet}\Large \textbf{Mohammad Reza Daneshvar Garmroodi}}
		
		{\color{blue}\small \href{mailto:Mohammadrezadaneshvar1994@gmail.com}{Mohammadrezadaneshvar1994@gmail.com}} \\
		
		{\color{blue}\small \href{https://,rdanesh.github.io}{MRDanesh.github.io}}
	\end{center}
	 
	
	
	\vspace{3mm}
	
	
	\noindent \textbf{\color{violet} EDUCATION}
	
	\vspace{-2mm}
	
	\noindent\rule[0.5ex]{\linewidth}{1pt}
	
	
		{\noindent  \bf Concordia University, Montreal, Canada} \hfill {\em Sep 2019 - May 2025} 
		\\ \textit{Ph.D. in Mechanical Engineering}
		
		\vspace{1.5mm}
		
		{\noindent  \bf Amirkabir University of Technology, Tehran, Iran} \hfill {\em Sep 2017 - Aug 2019} 
		\\ \textit{MSc in Mechanical Engineering}
	
		\vspace{1.5mm}
		
		{\noindent \bf University of Tabriz, Tabriz, Iran} \hfill {\em Sep 2013 - Aug 2017} 
		\\ \textit{BSc in Mechanical Engineering}
		
		
		%%%%%%%%%%%%%%%%%%%%%%%
		\vspace{2.5mm}
		
		
		\noindent \textbf{\color{violet} PROFESSIONAL EXPERIENCE}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		
		{\noindent  \bf Postdoctoral Researcher, Montreal, Canada} \hfill {\em May 2025 - present} 
		
		$\bullet$ Jet mixing and turbulent non-Newtonian flows, in collaboration with \textit{SINTEF }

		$\bullet$ Thermal convection in Micro-encapsulated PCM suspensions, in collaboration with \textit{Université de Lorraine} 
		
		\vspace{2.5mm}
		%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\noindent \textbf{\color{violet} PEER-REVIEWED PUBLICATIONS}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		
		
		\noindent {M.M. Nasiri, \textbf{M.R. Daneshvar Garmroodi} and M. Tembely. Elasto-Capillary dynamics of a viscoelastic hallow droplet,\textit{ Under Preparation}}.
		
		\noindent {\textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli. Two-dimensional mixing stirred system, mixing regimes and transitions.\textit{ Under Preparation}}.
		
		\noindent \href{https://arxiv.org/pdf/2503.09359}{\textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli. Yield-Stress Fluid Mixing: Localization Mechanisms and Regime Transitions.\textit{ Under Review with positive feedback, Journal of Fluid Mechanics.}}.
		
		\noindent \href{https://doi.org/10.1016/j.jnnfm.2024.105196}{\textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli. Mixing in heterogeneous fluids: An examination of fluid property variations.\textit{ Journal of Non-Newtonian Fluid Mechanics.}}
		
		
		%\noindent 3. {\textbf{M.R. Daneshvar Garmroodi}, Ida Karimfazli. Localization of stirring flows: the effect of the yield stress.\textit{ 8TH PACIFIC RIM CONFERENCE ON RHEOLOGY, 2023} . \href{https://indico.cern.ch/event/1216697/contributions/5286939/attachments/2599381/4487900/PRCR_Daneshvar.pdf}{({Article's Link})}}
		
		%\noindent 4. {\textbf{M.R. Daneshvar Garmroodi}, Ida Karimfazli. Chaotic mixing of complex fluids: on the effects of viscosity ratio.\textit{ The Canadian Society for Mechanical Engineering International Congress, 2022} . \href{https://era.library.ualberta.ca/items/c6928cbc-2bf4-455f-a94b-9ddf35ea13d2/download/8f2a7e76-7906-44ed-887e-141cfc8cb6d1}{({Article's Link})}}
		
		%\noindent 5. {\textbf{M.R. Daneshvar Garmroodi}, Ida Karimfazli. Mixing of complex fluids: on the effects of inhomogeneity.\textit{ The Canadian Society for Mechanical Engineering International Congress, 2021} . \href{https://library.upei.ca/islandora/object/csme2021\%3A18/datastream/PDF/download/csme2021\%3A18.pdf}{({Article's Link})}}
		
		\noindent \href{https://doi.org/10.1016/j.petrol.2020.107458}{\textbf{M.R. Daneshvar Garmroodi} and A. Ahmadpour. Numerical simulation of stratified waxy crude oil and water flows across horizontal pipes in the presence of wall heating.\textit{ Journal of Petroleum Science and Engineering, 193:107458, 2020}}
		
		\noindent  \href{https://doi.org/10.1016/j.cherd.2020.04.017}{\textbf{M.R. Daneshvar Garmroodi} and A. Ahmadpour. A numerical study on two-phase core-annular flows of waxy crude oil/water in inclined pipes.\textit{ Chemical Engineering Research and Design, 159:362
				– 376, 2020}}.
		
		\noindent \href{https://doi.org/10.1016/j.ijmecsci.2018.10.037}{\textbf{M.R. Daneshvar Garmroodi}, A. Ahmadpour, and F. Talati. MHD mixed convection
			of nanofluids in the presence of multiple rotating cylinders in different configurations:
			a two-phase numerical study.\textit{ International Journal of Mechanical Sciences, 150:247
				– 264, 2019}}
		
		\noindent  \href{https://link.springer.com/article/10.1007/s10973-019-09045-3}{\textbf{M.R. Daneshvar Garmroodi}, A. Ahmadpour, M. R. Hajmohammadi, and S. Gholamrezaie. Natural convection of a non-Newtonian ferrofluid in a porous elliptical enclosure in the presence of a non-uniform magnetic field.\textit{ Journal of Thermal Analysis and Calorimetry, 1-17, 2019}}
		
		\vspace{3mm}
		
		\noindent \textbf{\color{violet}CONTRIBUTED TALKS}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Mixing Yield-Stress Fluids: Localization Mechanisms and Regime Transitions, \textit{Second European Fluid Dynamics Conference  (EFDC2)}, Dublin, Ireland, August 2025.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Fluid mechanics of mixing in a two-dimensional stirred: regimes and mechanisms, \textit{The Canadian Society for Mechanical Engineering International Congress}, Montreal, Canada, May 2025.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Scalar mixing in viscoplastic fluids, \textit{26th International Conference of the Theoretical and Applied Mechanics (ICTAM 2024)}, Daegu, Republic of Korea, August 2024.
		
		\noindent  \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Understanding Mixing Dynamics in Yield Stress
		Fluids, \textit{The Canadian Society for Mechanical Engineering International Congress}, Toronto, Canada, May 2024.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Scalar mixing in viscoplastic fluids, \textit{The annual European rheology conference}, Leeds, United Kingdom, April 2024.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Localization of stirring flows: the effect of the yield stress, \textit{8th PACIFIC RIM conference on rheology}, Vancouver, Canada, May 2023.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Chaotic mixing of complex fluids: on the effects of viscosity ratio, \textit{The Canadian Society for Mechanical Engineering International Congress}, Edmonton, Canada, May 2022.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Mixing of heterogeneous fluids: buoyancy effects, \textit{The annual European rheology conference}, Seville, Spain, April 2022.
		
		\noindent \textbf{M.R. Daneshvar Garmroodi} and I. Karimfazli, Mixing of complex fluids: on the effects of inhomogeneity. \textit{The Canadian Society for Mechanical Engineering International Congress}, May 2021.
		
		\vspace{4mm}
		
		\vspace{1.5mm}
		
		\noindent \textbf{\color{violet} HONORS \& AWARDS}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
	\noindent \textbf {\small  Graduate Fellowship for Ph.D. program in Mechanical Engineering, Concordia University.} \hfill {Fall 2019} 
		\\ \textit{Four years, Monetary value: 37,915 CAD}
		
	
		
	\noindent \textbf {\small Graduate Fellowship for Ph.D. program in Marine Engineering, NTNU University.} \hfill {Fall 2019} 
		\\ \textit{three years, Monetary value 479,600 NOK (approximately 70,000 CAD per year), declined.}
		
		
	\noindent \textbf {\small  Graduate Fellowship for Ph.D. program in Mechanical Engineering, Ghent University.} \hfill {Fall 2019} 
		\\ \textit{three years, Monetary value 30,000 Euro per year, declined.}
		
			
	\noindent \textbf {\small Ranked 1st Among 60 Mechanical Engineering Master students of Amirkabir University.} \hfill {Spring 2019} 
		\\ \textit{four years, Monetary value: 300,000,000 Rial (approximately 7,000 CAD per year), declined.}
		
		
	\noindent \textbf {\small Accepted in the First Stage of the National Computer and Mathematical Olympiads.} \hfill {Fall 2010, 2011, 2012} 
		\vspace{1.5mm}
		
		
		
		\noindent \textbf{\color{violet}TEACHING}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		{\noindent  \bf Instructor, SuperKids, Montreal, Canada} \hfill {\em 2024-present} 
		\\ \textit{Teaching Linear Algebra, Calculus to high school and collage students}
		
		\vspace{1.5mm}
		
		{\noindent  \bf Teaching assistant, Concordia University, Montreal, Canada} \hfill {\em 2019-2025} 
		\\ \textit{Applied Advanced Calculus, Partial Differential Equations, Ordinary Differencial Equations, Fluid Mechanics I, Fluid Mechanics II, Heat Transfer I, Heat Transfer II, Thermodynamics I}
		
		\vspace{1.5mm}
		
		{\noindent  \bf Teaching assistant, Amirkabir University of Technology, Tehran, Iran} \hfill {\em 2017-2019} 
		\\ \textit{Fluid Mechanics, Heat Transfer I, Non-Newtonian Fluid Mechanics, Continuum Mechanics}
		
		%\vspace{1.5mm}
		
		%{\noindent $\bullet$ \bf Tutor of high school students, Tehran and Tabriz, Iran} \hfill {\em 2015-2019} 
		%\\ \textit{Physics, Mathematics}
		
		%\vspace{4mm}
		
		%\noindent WORKING EXPERIENCES
		
		%\vspace{-2mm}
		
		%\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		%{\noindent $\bullet$ \bf Software Engineering Intern in IranBar Company} \hfill {\em Summer 2018} 
		%\\ Writing the front-end of multiple pages using {React}, {Redux}, and {Sass}.
		
		
	
		

		

		
		%\vspace{4mm}
		
		%\noindent PROJECTS
		
		%\vspace{-2mm}
		
		%\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		%\noindent $\bullet$ Adding Dynamic Mesh to 'twoLiquidMixingFoam' solver in OpenFOAM.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ Simulation of Annular Flow of a Newtonian Fluid by Finite Volume Method and Coding in MATLAB.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ Simulation of Mixed Convection of Water Flows in a Lid-Driven Cavity by Finite Difference Method and Coding in MATLAB.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ ”A Priory" and ”A Posteriori” Tests Using Dynamic Smagorinsky, and Wong LES Models and Solving Filtered Burgers’ equation by Finite Difference Method in MATLAB.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ Calculating Pressure Drop and Volume Fraction for Two-Phase Gas-Water Flow in an Inclined Pipe by Martinelli and Drift Flux Correlations in C++.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ Approximate Solution for Boundary Layer of a Power law Fluid Over a Flat Plate in MATLAB.
		
		%\vspace{1.5mm}
		
		%\noindent $\bullet$ Numerical Solution of Transient One Dimensional Heat Conduction in a Fin with a Temperature dependent Thermal Conductivity by Finite Difference Method and Using Crank-Nicolson and TDMA Methods in C.
		
		%\newpage

		
		
			
		\vspace{2mm}
			 
		
	
		
		
		
		\vspace{-2mm}
		
		
		
		\vspace{2mm}
		
		\noindent \textbf{\color{violet} SELECTED PROJECTS}
		
		\vspace{-2mm}
		
		\noindent\rule[0.5ex]{\linewidth}{1pt}
		
		{\noindent Numerical simulation of the impact of a hallow viscoelastic droplet on surface using Basilisk. 
		\hfill {\em 2025} 
		
		
		\vspace{0.5mm}
		
		{\noindent Developing a CNN-LSTM Neural Network to Predict Flow Development
			\hfill {\em 2023} 
			
			
		{\noindent  Adding dynamic mesh and tracking passive particles in the twoLiquidMixingFoam solver in OpenFOAM
	    \hfill {\em 2021}  
	
	\vspace{0.5mm}
	
	{\noindent  Developing a melting solver in OpenFOAM Based on phase field and enthalpy methods
		\hfill {\em 2024} 
		
		\vspace{1.5mm}
		
		{\noindent Coding annular flow of a Newtonian fluid by finite volume SIMPLE method in MATLAB  
			\hfill {\em 2019} 
			
	\vspace{1.5mm}
	
	{\noindent  Coding mixed convection in a lid-driven cavity using streamfunction-vorticity by finite difference method
		\hfill {\em 2019} 
		
		\vspace{1.5mm}
		
		{\noindent A priory and ”A Posteriori” tests using dynamic Smagorinsky, and Wong LES Models one the filtered Burgers’ equation by finite Difference Method
			\\ \textit{Large Eddy Simulation Course}
			\vspace{1.5mm}
			
			{\noindent $\bullet$ Coupling Level-Set method with VOF algorithm in OpenFOAM
				\\ \textit{Multiphase Flows Course}
				\vspace{1.5mm}
				
			%{\noindent $\bullet$ Calculating Pressure Drop and Volume Fraction for Two-Phase Gas-Water Flow in an Inclined Pipe by Martinelli and Drift Flux Correlations in C++
				%\\ \textit{Multiphase Flows Course}
				%\vspace{1.5mm}
				
				%{\noindent $\bullet$ Approximate Solution for Boundary Layer of a Power law Fluid Over a Flat Plate
				%	\\ \textit{Non-Newtonian Fluid Mechanics Course}
				%	\vspace{1.5mm}

\end{document}